Algorithmic model for N-GREEN optical ring

### 2017-10-20 Papier NGreen/model.tex
img dans papier model

@@

\maketitle
\section*{Problem}
The application we study takes place in the C-Ran context. We want to centralise calculations into a common data-center for an area of antennas distributed on the territory. The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring. We study here only the behaviour of the ring. First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.

>>>>

\graphicspath{{img/}}

@@

\maketitle
\section{Introduction}
Blabla sur le contexte du projet NGREEN

\section{Model}

  \subsection{Optical ring}
    Graphe oriente representant un anneau, definition des terme delay
  \subsection{Discrete time model}
    temps slotte correspondant a un tick d'horloge
  \subsection{Into the node : Two kind of traffics}
    Descripion buffers/ on prepare des conteneurs.definition des therme paquet slot buffers
    Description CRAN-BE, precision sur le modele de generation
    presentation des differentes politiques d'insertion.

  \subsection{Objectives}
    Etudier Le comportement de nos politiques
    Trouver une solution deterministe et etudier l'impact sur les BE

\section{Study of the different insertion policies}

  \subsection{Parameters}
  Peut etre attendre les resultats de youssef pour fixer les deadline et seuil d'envoi dans les simuls.
  \subsection{No management}
  \subsection{CRAN priority}
  Conclure que c'est pas top top, même si c'est clairement mieux en CRAN, et qu'on va faire du determinisme.

\section{Deterministic approach for 0 latency on CRAN}
  \subsection{Packing}
  \subsection{Spreading}
  Pour ces deux la, ecrire proprement les ``algos''
  \subsection{Impact on the BE}
  REsultats de simuls

The application we study takes place in the C-Ran context. We want to centralise calculations into a common data-center for an area of antennas distributed on the territory. The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring. We study here only the behaviour of the ring. First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.
